---
title: "Vignette for chat and set_api_key functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette for chat and set_api_key functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Chat)
```

# Screen titles and abstracts with OpenAI’s GPT models

This function takes a data frame of study details, constructs a prompt
for each study, and sends it to OpenAI’s GPT-3.5-turbo model, as
default, for a response. The function returns a tibble with the original
study details and the model’s response.

## Parameters

- `data`: A data frame containing the study details. Each row should represent a study and must have 'title' and 'abstract' columns.
- `prompt`: A string that will be prepended to the study details to form the prompt for the model.
- `model`: A string specifying the model to use. Default is "gpt-3.5-turbo".

## Returns

A tibble with the original study details and the model's response.

## Example

```{r, eval = FALSE}
prompt <- "Is this study about a Functional Family Therapy (FFT) intervention?"
loaded_objects <- load("./data/filges2015_dat_modified.rda")
data <- get(loaded_objects)
chat(data, prompt, model = "gpt-3.5-turbo")
```

# Output
```{r, eval = FALSE}
A tibble: 6 × 3
   Title                                     StudyID decision_gpt
   <chr>                                     <chr>   <chr>       
 1 Estimating and communicating prognosis i… 1       "No, this s…
 2 Self-Directed Behavioral Family Interven… 2       "No, this s…
 3 Frequency domain source localization sho… 3       "No, this s…
 4 A Review of: 'Kearney, C. A. (2010). Hel… 4       "No, this s…
 5 Topographic differences in the adolescen… 5       "No, this s…
 6 BOOK REVIEW                               6       "No, this s…
```

# Set API Key

This function sets the API key for the CHATGPT_KEY environment variable.
If the environment variable is not set, it prompts the user to enter the API key.

## Details

The function first checks if the "CHATGPT_KEY" environment variable is set. 
If it is not set, it prompts the user to enter the value for "CHATGPT_KEY" and sets the environment variable to the entered value.